The interactions of rational, pragmatic agents  \n lead to efficient language structure and use

### 2019-01-29 paper/paper.Rmd
updates to plots and add figs to repo for reproducibilityy

```{r plot-optimal-langs, fig.env = "figure*", fig.pos = "h", fig.width=8, fig.height=2, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "Optimal languages are more likely to contain ambiguous items as the amount of contextual information increases. Vertical axis shows the proportion of optimal languages that contain ambiguity. Horizontal axis shows the number of contexts in each condition (1-4). Red-line represents the optimal language under our Zipfian cross-entropy objective while the blue and red lines show optimal languages under speaker- and listener-only consideration."}

img <- png::readPNG("figs/fig1.png")
grid::grid.raster(img)
```

@@

```{r plot-optimal-use, fig.env = "figure*", fig.pos = "h", fig.width=6, fig.height=2.5, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "(A) shows the empirical probability that our speaker used an ambiguous utterance as a function of discourse position. (B) shows speaker effort across the three models. (C) shows the Cross-Entropy objective under our three speaker models."}
img <- png::readPNG("figs/discourse_grid_plot.png")
grid::grid.raster(img)
```

>>>>

```{r plot-optimal-langs, fig.env = "figure*", fig.pos = "h", fig.width=8, fig.height=2, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "Optimal languages are more likely to contain ambiguous items as the amount of contextual information increases. Vertical axis shows the proportion of optimal languages that contain ambiguity. Horizontal axis shows the number of contexts in each condition (1-4). Red-line represents the optimal language under our Zipfian cross-entropy objective while the blue and red lines show optimal languages under speaker- and listener-only consideration."}
img <- png::readPNG("figs/fig1.png")
grid::grid.raster(img)
```

@@

```{r plot-optimal-use, fig.env = "figure*", fig.pos = "h", fig.width=6, fig.height=2.5, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "(A) shows the empirical probability that our speaker used an ambiguous utterance as a function of discourse position. (B) shows speaker effort across the three models. (C) shows the Cross-Entropy objective under our three speaker models."}

img <- png::readPNG("figs/discourse_grid_plot.png")
grid::grid.raster(img)
```
